Minimizing post-shock forecasting error using disparate information

### 2020-07-22 manuscript/manuscript.tex
revisions to manuscript with typos fixed and simulations of model 1

% title
\title{Minimizing post-shock forecasting error using disparate information}
\author{Jilei Lin\thanks{jileil2@ilinois.edu}}
\author{Daniel J. Eck\thanks{dje13@illinois.edu}}
\affil{Department of Statistics, University of Illinois at Urbana-Champaign}

@@

\maketitle
\begin{abstract}
    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded. Three shock-effects estimators were constructed for minimizing average forecast risk. We proposed risk-reduction propositions providing conditions when our methodology works and estimators for risk-reduction quantities. Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential success of post-shock forecasts before the post-shock response is observed. The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best. Leave-one-out cross validation is proposed to estimate consistency of risk-reduction propositions and best consistency of voting the best shock-estimators, prospectively informing users of the probabilities that this prospective evaluation is consistent with the reality. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

In this article, we will assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure. Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}. However, our model formulation is more general than \cite{ramaswamy1993empirical} and our donor pool is formed from independent time series.
%The main idea of our methodology is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, which is added to the original forecast at the known shock time point. 
We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.  These adjustment strategies all target the mean of the shock-effect distribution. However, such an estimation strategy can reduce mean squared error (MSE) when variation in the shock-effect distribution is small relative to the mean. We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast. The involved parameters in the risk-reduction propositions and risk-reduction quantities can be estimated by a residual bootstrap procedure that we develop within. %These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques will work well before the post-shock response is observed. 
We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock-effect adjustment estimators without. This prospective assessment does not require the observation of the post-shock response. Our Monte Carlo simulation results show that the risk-reduction conditions are highly consistent when the model for the shock effects is identified well with appropriate covariates under a fixed design. We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020. We show that our proposed adjustment estimators yield much better results than no adjustment in this setting. We also use this example to demonstrate settings in which the shock-effect may be decomposed into separate estimable parts. We now motivate our framework for post-shock forecasting.

@@

We will suppose that specific interest is in forecasts to made after the occurrence of a structural shock. To gauge the performance of forecasts, we consider forecast risk in the form of mean squared error (MSE),
$$
  R_T = \frac{1}{T}\sum_{t=1}^T\E{\hat y_{1,t} - y_{1,t}}^2,
$$
and root mean squared error (RMSE), given by $\sqrt{R_T}$, in our analyses.

@@

Figure \ref{figure1} provides simple intuition of the practical usefulness of our proposed methodology. This figure depicts a time-series that experienced a shock at time point $T_1^*+1 = 126$. It is supposed that the researcher does not have any information beyond $T_1^*+1$, but does have observations of forty disparate time series that have previously undergone a similar shock for which post-shock responses are recorded. Similarity in this context means that the shock effects are random variables that from a common distribution.
%As we can see, the purple line provides a better prediction than the red line in this particular example. But we will justify later that consideration of estimated shock-effects will improve the prediction under certain conditions.
In this example, the mean of the estimated shock effects is taken as a shock-effect estimator for the time series under study. Forecasts are then made by adding this shock-effect estimator to the estimated response values obtained from the process that ignores the shock. It is apparent from Figure \ref{figure1} that adjusting forecasts in this manner 1) leads to a reduction in forecasting risk; 2) does not fully recover the true shock-effect. We evaluate the performance of this post-shock forecasting methodology throughout this article; we outline situations for when it is expected to work and when it is not.

@@

In this section, we will describe the assumed dynamic panel models for which 
post-shock aggregated estimators are provided. The basic structure of these models 
are the same, the differences between them lie in the setup of the shock effect 
distribution.

@@

We will investigate post-shock aggregated estimators in $\mc{M}_2$ 

@@

structure for $\gamma$ and $\delta$:

@@

     \Theta &= &\{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i, \gamma_i)\colon t= 1, \ldots, T_i, i = 2, \ldots, n +1\}.\\
    \Theta_1 &= &\{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i, \gamma_i)\colon t= 1, \ldots, T_i, i = 1\}.\label{parameter},

@@

Note that the two forecasts do not differ in their predictions for 
$y_{1,t}$, $t = 1,\ldots T_1^*$, they only differ in predicting 
$y_{1,T_1^*+1}$. Throughout the rest of this article we show that the collection of 
disparate time series $\{y_{i,t}, t = 2,\ldots,T_i, i = 1,\ldots,n\}$ has 
the potential to improve the forecasts for $y_{1, t}$ when $t > T_1^*$ under different 
circumstances for the dynamic panel model $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$. We specifically focus on predictions for $y_{1,T_1^*+1}$, the first post-shock response. It is important to note that in general $\hat{\alpha}$ 
is not a consistent estimator of the unobserved $\alpha_1$ nor does it converge 
to $\alpha_1$.  Despite these inferential shortcomings, adjustment of the forecast 
for $y_{1,T_1^*+1}$ through the addition of $\hat{\alpha}$ has 
the potential to lower forecast risk under several conditions corresponding to 
different estimators of $\alpha_1$. % which will be discussed shortly.

@@

We now construct the aggregate estimators of the shock effects that appear in 
Forecast 2. We use these to forecast response values $y_{1, t}$ when 
$t > T_1^*$, i.e., the time series of interest after the shock time where we 
assume that $T_1^*$ is known.  %Notice that the shock effect 
%for time series $1$ is typically unobserved. But we can gather knowledge from 
%disparate time series to construct some sort of estimators that may be helpful for 
%estimating $\E{\alpha_1}$. 
First, we introduce the procedures of parameter estimation for 
$\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ (see Section \ref{modelsetup}). 
Conditional on all regression parameters, previous responses, and covariates, 
the response variable $y_{i,t}$ in $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ 
has distribution 
$$
  y_{i,t} 
    \sim N(\eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i'\x_{i,t} 
      + \beta_i'\x_{i,t-1}, \sigma^2).
$$
For $i = 2, \ldots, n$, all parameters in this model will be estimated with ordinary least squares 
(OLS) using historical data of $t = 1, \ldots, n_i$. For $i = 1$, we estimate all the parameters but $\alpha_1$ using OLS procedures for $t=1, \ldots, T_1^*$. In particular, let $\hat{\alpha}_i$, $i = 2, \ldots, n+1$ be the OLS estimate 
of $\alpha_i$.  Note that parameter estimation 
for $\mc{M}_1$ is identically the same as $\mc{M}_{21}$ and $\mc{M}_{22}$.

Second, we introduce the candidate estimators for $\alpha_1$. Define the 
\emph{adjustment estimator} for time series $i=1$ by,
\begin{equation} \label{adjusted}
  \hat{\alpha}_{\text{adj}} = \frac{1}{n}\sum_{i=2}^{n+1}\hat{\alpha}_i,
\end{equation}
where the $\hat{\alpha}_i$s in \eqref{adjusted} are OLS estimators of all of 
the $\alpha_i$s.  We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for 
the unknown $\alpha_1$ term for which no meaningful estimation information 
otherwise exists. It is intuitive that $\hat{\alpha}_{\rm adj}$ should perform 
well under $\mc{M}_1$ where we assume that $\alpha_i$'s share the same mean 
for $i= 1, \ldots, n+1$. However, it can also be shown that 
$\hat{\alpha}_{\rm adj}$ may be less favorable in $\mc{M}_{21}$ 
and $\mc{M}_{22}$, which will be discussed in detail in Section \ref{properties}.

We also consider the \emph{inverse-variance weighted estimator} 
in practical settings where the $T_i$'s and $T_i^*$'s vary greatly across $i$. 
The inverse-variance weighted estimator is defined as 
\begin{align*}
  \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{U}_i'\mbf{U}_i)_{22}^{-1},
\end{align*}
 $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, 
$\hat{\sigma}_i$ is the residual standard error from OLS estimation, 
and $\mbf{U}_i$ is the design matrix for OLS with respect to time series 
for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation 
is required and the numerator and denominator terms are dependent in general. 
%It is hard to evaluate its expectation and variance. 
%But it is clear 
%that $\hat{\alpha}_{\rm IVW}$ will generally not be unbiased. 
However, $\hat{\alpha}_{\rm IVW}$ can be a reasonable estimator in 
practical settings. %when the change 
%point is not symmetric and/or there are some series with small or large number 
%of time points recorded. We will then investigate the performance of this 
%estimator in simulation (Section \ref{simulation}).
We do not provide closed form expressions for $\E{\hat{\alpha}_{\rm IVW}}$ 
and $\var{\hat{\alpha}_{\rm IVW}}$, empirical performance of 
$\hat{\alpha}_{\rm IVW}$ is assessed via Monte Carlo simulation 
(see Section \ref{simulation}).

@@

where $\otimes$ is the kronecker product, $\mbf{I}_2$ is the identity matrix with two rows, $\mbf{X}_1,\hat{\mbf{X}}_1(\mbf{W}) \in \R^{2 \times p}$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon 1_n'\mbf{W} = 1 \}$. 

@@

 \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*)  \quad i.e., \quad \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*} \text{ and } \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}

@@

In this section, we discuss the properties that are related to forecast-risk reduction. In discussion of risk, it is useful to derive expressions for expectation and variance of the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator.  The expression for the expectations are as follow,

@@

Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple risk-reduction conditions and invoke a method of comparison, although our primary interest is in reducing forecast risk. % for $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm wadj}$ to reduce risk, and make it more clear with respect to when one is better than the other. 
These conditions will be discussed in Section \ref{conditions} and Section \ref{comparisons}. Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below

@@

Proposition \ref{proprisk} tells that under $\mc{M}_1$ if the variance of the estimator is smaller than the squared mean of $\alpha_1$, those estimators will enjoy the risk reduction properties. Recalling from variance expression at the beginning of Section \ref{properties}, Proposition \ref{proprisk} shows that the risk-reduction condition is
\begin{align}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2} < \mu_{\alpha}^2 \label{riskconditionadj}
\end{align}

Condition (\ref{riskconditionadj}) implies two facts: (1) adjustment (Forecast 2) is preferable to no adjustment (Forecast 1) asymptotically in $n$ whenever $\mu_{\alpha} \neq 0$; (2) In finite donor pool settings, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to its variability and overall regression variability.   %This result is also intuitive. For example, if  $\mu_{\alpha}$ is large, Forecast 1 will definitely work poor because large  $\mu_{\alpha}$ implies shock effects that cannot be ignored.  See Section \ref{forecast} for forecast formulation for details.

For the weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$, if  $\mathbf{W}^*$ does not satisfy (\ref{SCM}), its unbiased properties for $\E{\alpha_1}$ should hold approximately when the fit in (\ref{W}) is appropriate as commented in Section \ref{constructionofestimators}. From Proposition \ref{proprisk} and the variance expression for $\hat{\alpha}_{\rm wadj}$, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$ is
\begin{equation} \label{varwadj}
\var{\hat{\alpha}_{\rm wadj}}
 = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 < \mu_{\alpha}^2.
\end{equation}
In this case, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to the weighted sum of variances for shock effects for other time series and overall regression variability.  However, the above criteria are generally difficult to evaluate in practice due to the term $\hat{\alpha}_{\rm wadj}$. Sections \ref{varbootstrap} and \ref{loocv} will provide a detailed treatment about how to deal with these technical inequalities in practice.

@@

As an alternative, we can derive similar risk-reduction conditions that are appropriate for this setting. By Lemma \ref{risklemma} (see Section \ref{proofs}) and risk decomposition, we will achieve risk-reduction as long as
\begin{align*}
 \E{\alpha_1^2}= \var{\alpha_1}+(\E{\alpha_1})^2
 &>\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
  &=\var{\hat{\alpha}_{\rm adj}} +  (\E{\hat{\alpha}_{\rm adj}}-\alpha_1)^2 \\
  &=\var{\hat{\alpha}_{\rm adj}} +  \var{\alpha_1} + (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
\end{align*}
The above inequality simplifies to 
\begin{equation} \label{ineq}
 (\E{\alpha_1})^2 >\var{\hat{\alpha}_{\rm adj}}+ (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
\end{equation}
We estimate \eqref{ineq} using the bootstrap and LOOCV techniques developed in Sections \ref{varbootstrap} and \ref{loocv}.

@@

As mentioned in Section \ref{constructionofestimators}, it is difficult to evaluate the expectation and variance of $\hat{\alpha}_{\rm IVW}$. We note that $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$. That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.  Methods for assessing these inequalities in practice are developed in Sections \ref{varbootstrap} and \ref{loocv}.
%We will discuss comparisons of adjustment estimators in the the next section.

>>>>

% title
\title{Minimizing post-shock forecasting error using disparate information}
\author{Jilei Lin\thanks{jileil2@ilinois.edu} }
\author{Daniel J. Eck\thanks{dje13@illinois.edu}}
\affil{Department of Statistics, University of Illinois at Urbana-Champaign}

@@

\maketitle
\begin{abstract}
    We developed a forecasting methodology for providing credible forecasts for the time series data that have undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded. Three shock-effects estimators were constructed for minimizing average forecast risk. We proposed risk-reduction propositions providing conditions when our methodology works and estimators for risk-reduction quantities. Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential success of post-shock forecasts before the post-shock response is observed. The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well. Leave-one-out cross validation is proposed to estimate correctness of risk-reduction propositions, prospectively informing users of the probabilities that this prospective evaluation is in line with the reality. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

In this article, we will assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure. Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}. However, our model formulation is more general than \cite{ramaswamy1993empirical} and our donor pool is formed from independent time series.
%The main idea of our methodology is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, which is added to the original forecast at the known shock time point. 
We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.  These adjustment strategies all target the mean of the shock-effect distribution. However, such an estimation strategy can reduce mean squared error (MSE) when variation in the shock-effect distribution is small relative to the mean. We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast. The involved parameters in the risk-reduction propositions and risk-reduction quantities can be estimated by a residual bootstrap procedure that we develop within. %These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques will work well before the post-shock response is observed. 
We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock-effect adjustment estimators. This prospective assessment does not require the observation of the post-shock response. Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design. We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020. We show that our proposed adjustment estimators yield much better results than no adjustment in this setting. We also use this example to demonstrate settings in which the shock-effect may be decomposed into separate estimable parts. We now motivate our framework for post-shock forecasting.

@@

We will suppose that specific interest is in forecasting the response after the occurrence of a structural shock. To gauge the performance of forecasts, we consider forecast risk in the form of mean squared error (MSE),
$$
  R_T = \frac{1}{T}\sum_{t=1}^T\E{\hat y_{1,t} - y_{1,t}}^2,
$$
and root mean squared error (RMSE), given by $\sqrt{R_T}$, in our analyses.

@@

Figure \ref{figure1} provides a simple intuition of the practical usefulness of our proposed methodology. This figure depicts a time series that experienced a shock at time point $T_1^*+1 = 126$. It is supposed that the researcher does not have any information beyond $T_1^*+1$, but does have observations of forty disparate time series that have previously undergone a similar shock for which post-shock responses are recorded. Similarity in this context means that the shock effects are random variables that from a common distribution.
%As we can see, the purple line provides a better prediction than the red line in this particular example. But we will justify later that consideration of estimated shock-effects will improve the prediction under certain conditions.
In this example, the mean of the estimated shock effects is taken as a shock-effect estimator for the time series under study. Forecasts are then made by adding this shock-effect estimator to the estimated response values obtained from the process that ignores the shock. It is apparent from Figure \ref{figure1} that adjusting forecasts in this manner 1) leads to a reduction in forecasting risk; 2) does not fully recover the true shock-effect. We evaluate the performance of this post-shock forecasting methodology throughout this article; we outline situations for when it is expected to work and when it is not.

@@

In this section, we will describe the assumed dynamic panel models for which 
post-shock aggregated estimators are provided. The basic structures of these models 
are the same, the differences between them lie in the setup of the shock effect 
distribution.

@@

We will investigate the post-shock aggregated estimators in $\mc{M}_2$ 

@@

structure for $\gamma_i$ and $\delta_i$:

@@

     \Theta &= &\{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i, \gamma_i)\colon t= 1, \ldots, T_i, i = 2, \ldots, n +1\},\\
    \Theta_1 &= &\{(\eta_i, \phi_i, \theta_i, \beta_i, \alpha_i, \mbf{x}_{i,t}, y_{i,t-1}, \delta_i, \gamma_i)\colon t= 1, \ldots, T_i, i = 1\},\label{parameter}

@@

Note that the two forecasts do not differ in their predictions for 
$y_{1,t}$, $t = 1,\ldots T_1^*$. Instead, they only differ in predicting 
$y_{1,T_1^*+1}$. Throughout the rest of this article we show that the collection of 
disparate time series $\{y_{i,t}, t = 2,\ldots,T_i, i = 1,\ldots,n\}$ has 
the potential to improve the forecasts for $y_{1, t}$ when $t > T_1^*$ under different 
circumstances for the dynamic panel model $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$. We specifically focus on predictions for $y_{1,T_1^*+1}$, the first post-shock response. It is important to note that in general $\hat{\alpha}$ 
is not a consistent estimator of the unobserved $\alpha_1$ nor does it converge 
to $\alpha_1$.  Despite these inferential shortcomings, adjustment of the forecast 
for $y_{1,T_1^*+1}$ through the addition of $\hat{\alpha}$ has 
the potential to lower forecast risk under several conditions corresponding to 
different estimators of $\alpha_1$. % which will be discussed shortly.

@@

We now construct the aggregate estimators of the shock effects that appear in 
Forecast 2 (see Section \ref{forecast}). We use these to forecast response values $y_{1, T_1^*+1}$ assuming that $T_1^*$ is known.  %Notice that the shock effect 
%for time series $1$ is typically unobserved. But we can gather knowledge from 
%disparate time series to construct some sort of estimators that may be helpful for 
%estimating $\E{\alpha_1}$. 
First, we introduce the procedures of parameter estimation for 
$\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ (see Section \ref{modelsetup}). 
Conditional on all regression parameters, previous responses, and covariates, 
the response variable $y_{i,t}$ in $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ 
has distribution 
$$
  y_{i,t} 
    \sim N(\eta_i + \alpha_iD_{i,t} + \phi_i y_{i,t-1} + \theta_i'\x_{i,t} 
      + \beta_i'\x_{i,t-1}, \sigma^2).
$$
For $i = 2, \ldots, n$, all parameters in this model will be estimated with ordinary least squares 
(OLS) using historical data of $t = 1, \ldots, n_i$. For $i = 1$, we estimate all the parameters but $\alpha_1$ using OLS procedures for $t=1, \ldots, T_1^*$. In particular, let $\hat{\alpha}_i$, $i = 2, \ldots, n+1$ be the OLS estimate 
of $\alpha_i$.  Note that parameter estimation 
for $\mc{M}_1$ is identically the same as that for $\mc{M}_{21}$ or $\mc{M}_{22}$.

Second, we introduce the candidate estimators for $\alpha_1$. Define the 
\emph{adjustment estimator} for time series $i=1$ by
\begin{equation} \label{adjusted}
  \hat{\alpha}_{\text{adj}} = \frac{1}{n}\sum_{i=2}^{n+1}\hat{\alpha}_i,
\end{equation}
where the $\hat{\alpha}_i$s in \eqref{adjusted} are OLS estimators of all of 
the $\alpha_i$s for $i = 2, \ldots, n+1$.  We can use $\hat{\alpha}_{\text{adj}}$ as an estimator for 
the unknown $\alpha_1$ term for which no meaningful estimation information 
otherwise exists. It is intuitive that $\hat{\alpha}_{\rm adj}$ should perform 
well under $\mc{M}_1$ where we assume that $\alpha_i$'s share the same mean 
for $i= 1, \ldots, n+1$. However, it can also be shown that 
$\hat{\alpha}_{\rm adj}$ may be less favorable in $\mc{M}_{21}$ 
and $\mc{M}_{22}$, which will be discussed in detail in Section \ref{properties}.

We also consider the \emph{inverse-variance weighted estimator} 
in practical settings where the $T_i$'s and $T_i^*$'s vary greatly across $i$. 
The inverse-variance weighted estimator is defined as 
\begin{align*}
  \hat{\alpha}_{\rm IVW} = \frac{\sum_{i=2}^{n+1} \hat{\alpha}_i / \hat{\sigma}_{i\alpha}^2}{\sum_{i=2}^{n+1} 1/\hat{\sigma}_{i\alpha}^2},
  \quad \text{ where } \quad  \hat{\sigma}_{i\alpha}^2 = \hat{\sigma}^2_i( \mathbf{U}_i'\mbf{U}_i)_{22}^{-1},
\end{align*}
where  $\hat{\alpha}_i$ is the OLS estimator of $\alpha_i$, 
$\hat{\sigma}_i$ is the residual standard error from OLS estimation, 
and $\mbf{U}_i$ is the design matrix for OLS with respect to time series 
for $i = 2, \ldots, n+1$. Note that since $\sigma$ is unknown, estimation 
is required and the numerator and denominator terms are dependent in general. 
%It is hard to evaluate its expectation and variance. 
%But it is clear 
%that $\hat{\alpha}_{\rm IVW}$ will generally not be unbiased. 
However, $\hat{\alpha}_{\rm IVW}$ can be a reasonable estimator in 
practical settings. %when the change 
%point is not symmetric and/or there are some series with small or large number 
%of time points recorded. We will then investigate the performance of this 
%estimator in simulation (Section \ref{simulation}).
We do not provide closed form expressions for $\E{\hat{\alpha}_{\rm IVW}}$ 
and $\var{\hat{\alpha}_{\rm IVW}}$ but empirical performance of 
$\hat{\alpha}_{\rm IVW}$ is assessed via Monte Carlo simulation 
(see Section \ref{simulation}).

@@

where $\otimes$ is the Kronecker product, $\mbf{I}_2$ is the identity matrix with two rows, and $\mbf{X}_1,\hat{\mbf{X}}_1(\mbf{W}) \in \R^{2 \times p}$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon 1_n'\mbf{W} = 1 \}$. 

@@

 \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*),  \quad i.e., \quad \mbf{x}_{1, T_1^*} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*} \text{ and } \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}

@@

In this section, we discuss the properties that are related to forecast-risk reduction. In discussion of risk, it is useful to derive expressions for expectation and variance of the adjustment estimator $\hat{\alpha}_{\rm adj}$ and weighted-adjustment estimator.  The expressions for the expectations are as follow,

@@

Unbiasedness properties for $\E{\alpha_1}$ of $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ allow for simple risk-reduction conditions, and more importantly motivates a bootstrap estimation for evaluation of these conditions. % for $\hat{\alpha}_{\rm adj}$ and  $\hat{\alpha}_{\rm wadj}$ to reduce risk, and make it more clear with respect to when one is better than the other. 
These conditions and bootstrap will be discussed in Section \ref{conditions} and \ref{varbootstrap}, respectively. Next, we present the variance expressions for $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ as below.

@@

Proposition \ref{proprisk} tells that under $\mc{M}_1$ if the variance of the estimator is smaller than the squared mean of $\alpha_1$, those estimators will enjoy the risk reduction properties. Recalling from variance expression at the beginning of Section \ref{properties}, Proposition \ref{proprisk} shows that the risk-reduction condition is
\begin{align}
  \var{\hat{\alpha}_{\rm adj}} 
  &=\frac{\sigma^2}{n^2}\sum_{i=2}^{n+1}\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\frac{\sigma^2_{\alpha}}{n^2} < \mu_{\alpha}^2. \label{riskconditionadj}
\end{align}

Condition (\ref{riskconditionadj}) implies two facts: (1) adjustment (Forecast 2) is preferable to no adjustment (Forecast 1) asymptotically in $n$ whenever $\mu_{\alpha} \neq 0$ (see Forecast in Section \ref{forecast}); (2) In finite donor pool settings, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to its variability and overall regression variability.   %This result is also intuitive. For example, if  $\mu_{\alpha}$ is large, Forecast 1 will definitely work poor because large  $\mu_{\alpha}$ implies shock effects that cannot be ignored.  See Section \ref{forecast} for forecast formulation for details.

For the weighted-adjustment estimator $\hat{\alpha}_{\rm wadj}$, if  $\mathbf{W}^*$ does not satisfy (\ref{SCM}), its unbiased properties for $\E{\alpha_1}$ should hold approximately when the fit in (\ref{W}) is appropriate as commented in Section \ref{constructionofestimators}. From Proposition \ref{proprisk} and the variance expression for $\hat{\alpha}_{\rm wadj}$, the risk-reduction condition for $\hat{\alpha}_{\rm wadj}$ is
\begin{equation} \label{varwadj}
\var{\hat{\alpha}_{\rm wadj}}
 = \sigma^2\sum_{i=2}^{n+1}(w_i^*)^2\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}+\sigma^2_{\alpha}\sum_{i=2}^{n+1}(w_i^*)^2 < \mu_{\alpha}^2.
\end{equation}
In this case, adjustment is preferable to no adjustment when $\mu_{\alpha}$ is large relative to the weighted sum of variances for shock effects for other time series and overall regression variability.  However, the above criteria are generally difficult to evaluate in practice due to the term $\mrm{E}\big\{(\mbf{U}'_i\mbf{U}_i)^{-1}_{22}\big\}$.

In fact, we can extend checking risk-reduction conditions to verifying the sign of risk-reduction quantities for generalization. For an adjustment estimator $\hat{\alpha}$, the risk-reduction quantity is defined as  $\Delta(\hat{\alpha})=R_{T_1^*+1,1}-R_{T_1^*+1,2}$. If $\Delta(\hat{\alpha})>0$, $\hat{\alpha}$ will improve the Forecast 1. In this context, according to Proposition \ref{proprisk}, under $\mc{M}_1$, $\Delta(\hat{\alpha}_{\rm adj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm adj}}$ and $\Delta(\hat{\alpha}_{\rm wadj})= \mu_{\alpha}^2-\var{\hat{\alpha}_{\rm wadj}}$. Sections \ref{varbootstrap} and \ref{loocv} will provide a detailed treatment about how to checking the sign  in practice.

@@

As an alternative, we can derive similar risk-reduction conditions that are appropriate for this setting. By Lemma \ref{risklemma} (see Section \ref{proofs}) and risk decomposition, we will achieve risk-reduction as long as
\begin{align*}
 \E{\alpha_1^2}= \var{\alpha_1}+(\E{\alpha_1})^2
 &>\E{\hat{\alpha}_{\rm adj}-\alpha_1}^2\\
  &=\var{\hat{\alpha}_{\rm adj}} +  (\E{\hat{\alpha}_{\rm adj}}-\alpha_1)^2 \\
  &=\var{\hat{\alpha}_{\rm adj}} +  \var{\alpha_1} + (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
\end{align*}
The above inequality simplifies to 
\begin{equation} \label{ineq}
 (\E{\alpha_1})^2 >\var{\hat{\alpha}_{\rm adj}}+ (\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2.
\end{equation}

@@

As mentioned in Section \ref{constructionofestimators}, it is difficult to evaluate the expectation and variance of $\hat{\alpha}_{\rm IVW}$. We note that $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$. That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.  Therefore, using the generalization mentioned in Section \ref{conditionsmodel1}, under $\mc{M}_2$, it can be shown that the risk-reduction quantities are
\begin{align*}
  \Delta(\hat{\alpha}_{\rm adj}) 
  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}}-(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2\\
  \Delta(\hat{\alpha}_{\rm IVW}) 
  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}}-(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2\\
  \Delta(\hat{\alpha}_{\rm wadj}) 
  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}},
\end{align*}
where we estimate $\Delta(\hat{\alpha})$  using the bootstrap and LOOCV techniques developed in Sections \ref{varbootstrap} and \ref{loocv}.
